\sysfull

### 2018-04-16 paper/paging.tex
paging
motivating paging

>>>>

\textcolor{red}{[additional motivation for coala memory virtualization] we should emphasize that Coala programming model removes the burden of identifying the write-after-read dependencies from the programmer  as compared to Chain. And it does not require a specific compiler that cannot consider a runtime dependent behavior like Interrupts service handling to guarantee memory protection, as in Alpaca.}
